\chapter{Identification of stakeholders and design concerns} \label{chp:identification-of-stakeholders-and-design-concerns}
	\begin{comment}
		An SDD shall identify the design stakeholders for the design subject.
		An SDD shall identify the design concerns of each identified design stakeholder.
		An SDD shall address each identified design concern.
		NOTE—An SDD can be used to satisfy the content guidelines for several types of design description as defined in
		ISO/IEC 15289:2006 [B25], by identifying their content guidelines as design concerns. The types of design
		descriptions are as follows: database design description (10.14),6 database detailed design description (10.15), highlevel
		software design description (10.22), interface description (10.27), low-level software design description (10.29),
		system description (10.71), and system element description (10.72).
	\end{comment}

	There are many different potential users of \emph{Computational Library}. The most of them should have a basic knowledge about computer science, algorithms and complexities. Mentioned domains and fields of science are very desire in terms of quick and correct usage of library. Their knowledge will help them understand design patterns behind the implementations as well. Distinguishing some of them as follows: 
	\begin{itemize}
		\item programmers;
		\item researchers;
		\item scientists;
		\item others.
	\end{itemize}
	Performance of the computational library has big impact on the potential commerce use in scientific environment. The testability and convenient in use is also very strong factor of popularity of scientific computational libraries. 
	
	Designing computational libraries is extremely hard, because problem involves both memory and computational problems that should be faced. It is very common that by reducing one of them we also increase the second, giving us the problem of finding the balance between those complexities. When it comes to computational libraries it is also very hard to choose the scope of the problem that it should solve. The smaller and less generic problem is the more efficient our solution can be, which of course does not apply for all the problems. In terms of the problem described in Section \ref{s:introduction:purpose} it can be assumed that the problem of this library is very narrow, which gives opportunity to design and implement very efficient solution.
\chapter{Templates} \label{Template viewpoint-view design label}
%\input{chapters/viewpoints-views/template-design-viewpoint-view}

\input{chapters/viewpoints/templates/context-viewpoint-template}
\input{chapters/viewpoints/templates/composition-viewpoint-template}
\input{chapters/viewpoints/templates/logical-viewpoint-template}
\input{chapters/viewpoints/templates/dependency-viewpoint-template}
\input{chapters/viewpoints/templates/information-viewpoint-template}
\input{chapters/viewpoints/templates/patterns-viewpoint-template}
\input{chapters/viewpoints/templates/interface-viewpoint-template}
\input{chapters/viewpoints/templates/structure-viewpoint-template}
\input{chapters/viewpoints/templates/interaction-viewpoint-template}
\input{chapters/viewpoints/templates/state-dynamics-viewpoint-template}
\input{chapters/viewpoints/templates/algorithm-viewpoint-template}
\input{chapters/viewpoints/templates/resources-viewpoint-template}


\input{chapters/views/template/view-template}
