\section{Reporting Feature} \label{s:system-features:reporting-feature}
	\begin{comment}
		$<$Don’t really say “System Feature 1.” State the feature name in just a few 
		words.$>$
	\end{comment}

\subsection*{Description and Priority}
	\begin{comment}
		$<$Provide a short description of the feature and indicate whether it is of 
		High, Medium, or Low priority. You could also include specific priority 
		component ratings, such as benefit, penalty, cost, and risk (each rated on a 
		relative scale from a low of 1 to a high of 9).$>$
	\end{comment}
	\textsc{Priority: } Very High \\
	The output of the simulation is in form of report, which should contain all the necessary information for comparison of accounting practices.
	
\subsection*{Stimulus/Response Sequences}
	\begin{comment}
		$<$List the sequences of user actions and system responses that stimulate the 
		behavior defined for this feature. These will correspond to the dialog elements 
		associated with use cases.$>$
	\end{comment}

	\stimresp
	{User requests for queue statistics, for example: \gls{throughput}, average waiting time or \gls{turnaroundRatio}.}
	{Each of queues in the system tracks changes in waiting and executing areas.}
	
	\medskip
	
	\stimresp
	{User requests for machine statistics, for example: working and idle time.}
	{Simulation will track changes in time for each job. This data will be compared at the end of a simulation with a queue statistics.}
	
	\medskip
	
	\stimresp
	{User requests for financial statistics, for example: resulting price paid by the users, operating costs or total income.}
	{Accounting will be made for each user. Operating costs and total income will be calculated.}
\subsection*{Functional Requirements}
	\begin{comment}
		$<$Itemize the detailed functional requirements associated with this feature.  
		These are the software capabilities that must be present in order for the user 
		to carry out the services provided by the feature, or to execute the use case.  
		Include how the product should respond to anticipated error conditions or 
		invalid inputs. Requirements should be concise, complete, unambiguous, 
		verifiable, and necessary. Use “TBD” as a placeholder to indicate when necessary 
		information is not yet available.$>$
		
		$<$Each requirement should be uniquely identified with a sequence number or a 
		meaningful tag of some kind.$>$
		
		REQ-1:	REQ-2:
	\end{comment}

	\begin{functional}{Queue Statistics}{Medium}{None}
		\label{fn:reporting-feature:queue-statistics}
		\term{DESC}
		{
			Simulation report should contain following queue statistics:
			\begin{itemize}
				\item \gls{throughput};
				\item average waiting time;
				\item \gls{turnaroundRatio}
			\end{itemize}
		}
		\term{RAT}{In order to provide queue statistics.}
	\end{functional}

	\begin{functional}{Machine Statistics}{Medium}{None}
		\label{fn:reporting-feature:machine-statistics}
		\term{DESC}
		{
			Simulation report should contain following machine statistics:
			\begin{itemize}
				\item working time;
				\item idle time.
			\end{itemize}
		}
		\term{RAT}{In order to provide machine statistics.}
	\end{functional}

	\begin{functional}{Financial Statistics}{High}{None}
		\label{fn:reporting-feature:financial-statistics}
		\term{DESC}
		{
			Simulation report should contain following financial statistics:
			\begin{itemize}
				\item resulting price paid by the users;
				\item operating costs;
				\item \gls{economicBalance}.
			\end{itemize}
		}
		\term{RAT}{In order to provide financial statistics.}
	\end{functional}

	\begin{functional}{Check Statistics}{Medium}
		{
			\ref{fn:reporting-feature:financial-statistics},
			\ref{fn:reporting-feature:machine-statistics},
			\ref{fn:reporting-feature:queue-statistics}
		}
		\label{fn:reporting-feature:check-statistics}
		\term{DESC}
		{
			Report should contain all the fields described in depended requirements.
		}
		\term{RAT}{In order to provide full report.}
	\end{functional}