\chapter{Details of the Level Test Design} \label{chp:details-of-the-level-test-design}
	\begin{comment}
		Introduce the following subordinate sections. This section describes the features to be tested and any
		refinements to the test approach as required for the level. It also identifies the sets of test cases (highest
		level test cases) or scenarios along with the pass/fail criteria. It may also include the test deliverables.
	\end{comment}
	Tests of performance level described in this document have different types, distinguishing:
	\begin{itemize}
		\item data type deviation comparison;
		\item data type speed-up comparison;
		\item \gls{cuda} speed-up comparison;
		\item \gls{openmp} threads factor comparison;
		\item cumulative comparison.
	\end{itemize}
	All of presented before types of performance test can be also performed for both \gls{CRS} and \gls{ELL} matrix storage formats.
\section{Features to be tested} \label{s:details-of-the-level-test-design:features-to-be-tested}
	\begin{comment}
		Identify the test items and describe the features and combinations of features that are the object of this
		LTD. Other features that may be exercised but that are not the specific object of this LTD need not be
		identified (e.g., a database management system that is supporting the reports that are being tested). The
		LTD provides more detailed information than the Level Test Plan. For example, identify an overall test
		architecture of all test scenarios, the individual scenarios, and the detailed test objectives within each
		scenario.
		For each feature or feature combination, a reference to its associated requirements in the item
		requirement and/or design description may be included. This may be documented in a Test
		Traceability Matrix (LTP Section 2.2).
	\end{comment}
	Performance tests described in this document focus on the computational routines, hence according to the \gls{SRS} document it is possible to distinguish requirements from following sections:
	\begin{itemize}
		\item
		{
			\textbf{4.1 Common Feature}
			\begin{itemize}
				\item \textbf{FN--4.1.4} \emph{Computing matrix--vector dot product using \gls{CRS}}
				\item \textbf{FN--4.1.5} \emph{Computing matrix--vector dot product using \gls{ELL}}
			\end{itemize}
		}
		\item
		{
			\textbf{4.2 \gls{openmp} Feature}
			\begin{itemize}
				\item \textbf{FN--4.2.6} \emph{Computing matrix--vector dot product using \gls{CRS} and \gls{openmp}}
				\item \textbf{FN--4.2.7} \emph{Computing matrix--vector dot product using \gls{ELL} and \gls{openmp}}
			\end{itemize}
		}
		\item
		{
			\textbf{4.3 \gls{cuda} Feature}
			\begin{itemize}
				\item \textbf{FN--4.3.8} \emph{Computing matrix--vector dot product using \gls{CRS} and \gls{cuda}
				\item \textbf{FN--4.3.9} \emph{Computing matrix--vector dot product using \gls{ELL} and \gls{cuda}}}
			\end{itemize}
		}
	\end{itemize}
\section{Approach refinements} \label{s:details-of-the-level-test-design:approach-refinements}
	\begin{comment}
		Specify refinements to the approach described in the corresponding Level Test Plan (if there is one;
		otherwise specify the entire approach). Include specific test techniques to be used. The method of
		analyzing test results should be identified (e.g., comparator tools, visual inspection, etc.).
		Summarize the common attributes of any test cases. This may include input constraints that must be
		true for every input in a set of associated test cases, any shared environmental needs, any shared
		special procedural requirements, and any shared case dependencies. Sets of associated test cases may
		be identified as scenarios (also commonly called scripts or suites). Test scenarios should be designed to
		be as reusable as possible for regression testing, revalidation testing for changes, and training new
		employees who must either use or support the system over time.
	\end{comment}
	Approach of testing performance of implemented routines is described in details in Chapter \ref{s:details-of-the-level-test-design:features-to-be-tested}, \gls{MTP} and \gls{SRS} within requirements described in Chapter 5 (\emph{Other Nonfunctional Requirements}). Test scenarios and test suites does not require iterative approach, but it is very important to test various test data from different sources. It is also not necessary to run all test cases if there is no need to do it, because it consumes a lot of time.
\section{Test identification} \label{s:details-of-the-level-test-design:test-identification}
	\begin{comment}
		List the identifier and a brief description of each test case (or set of related test cases) in scenarios for
		this design. A particular test case, scenario, or procedure may be identified in more than one LTD. List
		the identifier and a brief description of each procedure associated with this LTD.
	\end{comment}
	Each test suite should have a unique name with a brief description of the tested domain. Similarly to mentioned test suites each test scenario also should have the same fields, but more detailed description should be introduced. Example of test identification should look in a following manner: \\
	\begin{center}
		\boxed
		{
			\begin{tabular}{ll}
				\textsc{Identification:} & Configuration Main Test Suite \\
				\textsc{Description:} & Contains all the tests related to the configuration.
			\end{tabular}
		}
	\end{center}
\section{Feature pass/fail criteria} \label{s:details-of-the-level-test-design:feature-pass-fail-criteria}
	\begin{comment}
		Specify the criteria to be used to determine whether the feature or feature combination has passed or
		failed. This is commonly based on the number of anomalies found in each severity category(s). This
		section is not needed if it is covered by an MTP and there have been no subsequent changes to the
		criteria.
	\end{comment}
	In case of performance-tests there is very complex way to describe fail or pass criteria. In a general way we can say that if results of the tests is below acceptable threshold the test is marked as a fail. 
	
	In terms of the assignment the performance test described has more academic approach and all the data is used as a reference for other future implementations. Summarizing only unexpected errors can mark a performance test as a fail. For example it concerns memory allocation or not supported driver/hardware issues.
\section{Test deliverables} \label{s:details-of-the-level-test-design:test-deliverables}
	\begin{comment}
		Identify all information that is to be delivered by the test activity (documents, data, etc.). The following
		documents may be included:
		⎯ Level Test Plan(s)
		⎯ Level Test Design(s)
		⎯ Level Test Cases
		⎯ Level Test Procedures
		⎯ Level Test Logs
		⎯ Anomaly Reports
		⎯ Level Interim Test Status Report(s)
		⎯ Level Test Report(s)
		⎯ Master Test Report
		Test input data and test output data may be identified as deliverables. Test tools may also be included.
		If documents have been combined or eliminated, then this list will be modified accordingly.
		Describe the process of delivering the completed information to the individuals (preferably by position,
		not name) and organizational entities that will need it. This may be a reference to a Configuration
		Management Plan. This delivery process description is not required if it is covered by the MTP and
		there are no changes
	\end{comment}
	Each of test cases in performance test set should produce a set of performance metrics such as:
	\begin{itemize}
		\item average time of kernel execution;
		\item number of \gls{FLOPS};
		\item in some cases deviation from the analytic solution;
		\item comparison of deviation between different data types precision.
	\end{itemize}